### 2015-05-08 paper/review-progress.Rmd
update to do
removed the shortages section

@@

From Luke

>>>>

### TODO

- Drop a plot or two (dropped shortages plot)
- Make circles same size in dotplots, add error bars
- Add histograms as subplots to facets for time spent studying (Not possible, se bands have been added)
- paragraph on fishing (Di)
- Clean language on middle east surprise
- Age started vs years in school

### My email to Brian Tarran

@@

### From Luke
